\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{parskip}

\geometry{left=1.2cm, right=1.2cm, top=1.2cm, bottom=1.2cm}

\definecolor{linkblue}{RGB}{0, 102, 204}
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue
}

\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{10pt}{4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Shaurya Sarswat}}\\
    \vspace{2pt}
    \faPhone~+91-9411071990 \quad
    \faEnvelope~\href{mailto:shauryasarswat2024@gmail.com}{shauryasarswat2024@gmail.com} \quad
    \faLinkedin~\href{https://linkedin.com/in/ShauryaSarswat}{LinkedIn} \quad
    \faGithub~\href{https://github.com/ShauryaSarswat}{GitHub} \quad
    \href{https://portfolio-silk-alpha-44.vercel.app}{Portfolio} \quad
    \href{https://leetcode.com/ShauryaSarswat}{LeetCode}
\end{center}

\vspace{5pt}

\section*{Education}
\textbf{Dr. A.P.J. Abdul Kalam Technical University} \hfill July 2020 – July 2024 \\
Bachelor of Technology in Computer Science \hfill CGPA: 8.43

\section*{Experience}

\textbf{Curelink} \hfill Jun 2024 – Present \\
\textit{Business Analyst} – Gurugram, India
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Extracted and analyzed data using Metabase, PostgreSQL, and Excel to generate actionable insights, contributing to a 10\% month-over-month revenue increase.
    \item Built automated dashboards in Metabase to track onboarding SOPs, raising completion from 30\% to 57\%.
    \item Authored PRDs to automate lead assignment and streamline onboarding (e.g., reducing lead wait time by 80\%).
    \item Conducted QA for field sales, delivering training that led to 10\% MoM revenue growth.
    \item Reduced false leads from 17\% to 9\% and increased lead volume by 15\% via continuous optimization.
\end{itemize}

\textbf{Provis Technologies Pvt. Ltd.} \hfill Jul 2023 – Sep 2023 \\
\textit{Full-Stack Development Intern} – Jaipur, India
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Developed REST APIs using Node.js/Express.js for a blog web app.
    \item Built a highly interactive UI with React.js, improving user retention by 30\%.
    \item Tech stack: MongoDB, Express.js, React.js, Node.js.
\end{itemize}

\section*{Projects}

\textbf{Walmart Data Regression} \\
\textit{Python, ML, NumPy, Pandas, Scikit-learn, Matplotlib}
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Analyzed Walmart sales data using regression and deployed the notebook on Kaggle (1000+ views).
    \item Provided actionable insights on sales trends for business decisions.
\end{itemize}

\textbf{Vetan} \\
\textit{Python, ML, Streamlit, Pandas, Scikit-learn}
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Built a salary prediction app based on Stack Overflow survey.
    \item Achieved 95.7\% accuracy using Random Forest and deployed the front end with Streamlit.
\end{itemize}

\section*{Technical Skills}
Python, SQL, JavaScript, PostgreSQL, MySQL, Excel, Metabase, Tableau, Data Analytics, Machine Learning, REST API, Git, Linux, Pandas, NumPy, Matplotlib, Seaborn, Scikit-learn, Jupyter Notebooks, Data Visualization

\section*{Awards and Achievements}
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Qualified Meta Hacker Cup 2022 – Rank: 5363 (Qualifiers), 6019 (Round 1)
    \item AIR 149 in Newton School Coderush Contest
    \item Rank 1283 among 90,000+ in PrepSAT Hackathon (PrepInsta)
    \item Solved 1000+ DSA problems and earned 8 LeetCode badges
\end{itemize}

\section*{Extracurriculars}
\textbf{MITGI Voyager – Chief Editor (2023–2024)}
\begin{itemize}[itemsep=2pt, leftmargin=0pt]
    \item Led a 12-member editorial team and published 3 annual editions.
    \item Interviewed 20+ candidates and supervised magazine content development.
\end{itemize}

\end{document}
